Constant Error Tolerance Computational Fuzzy Extractors

### 2014-02-04 trunk/constantRate/ConstCompFuzzExt.tex

\subsection{Obfuscation}
Our construction uses obfuscation of point functions. This is the following family of functions:
\[
I_w(x):\begin{cases} 1 & x=w\\0 & \text{otherwise}\end{cases}.
\]
The notion of obfuscation required is virtual grey-box (VGB) introduced in \cite{bitansky2010strong}. This notion is weaker then the notion of virtual grey-box (\cite{barak2001possibility}) as it allows the simulator to run in unbounded time as long as it only makes polynomial number of oracle queries to the point function. In the following definition we also require that the obfuscation is composable and secure with respect to auxiliary input. Compassable auxiliary-input VGB obfuscators for point function are constructed in \cite[Theorem 6.1]{bitansky2010strong} from the Strong Vector Decision Difﬁe Hellman assumption which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points.

\begin{definition}[$t$-composable obfuscation VGB obfuscation with auxiliary input \cite{bitansky2010strong}]
\label{def:obf} Let $\mathcal{I}$ be a family of polynomial-size circuits.  A PPT algorithm $\mathcal{O}$ is a $t$-composable VGB obfuscator for $\mathcal{I}$ with auxiliary-input if the following conditions are met:
\begin{enumerate}
\item \emph{Functionality:} for every $I \in \mathcal{I}$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$
\item \emph{Virtual grey-box:}  For every PPT adversary $A$ and polynomial $p$, there exists a (possibly inefficient) simulator $S$ and a polynomial $q$ such that for all sufficiently large $n$, any  sequence of circuits $I^1,\dots,I^t \in \mathcal{I}_n$, (where $t=\poly(n)$) and for all auxiliary inputs $z\in \zo^*$:
\[
|\Pr_{A,\mathcal{O}}[A(z,\mathcal{O}(I^1),\dots,\mathcal{O}(I^t)) = 1] - \Pr_{S}[S^{(I^1,\dots,I^t)[q(n)]}(z, 1^{|I^1|},\dots,1^{|I^t|}) = 1] | < \frac{1}{p(n)} \enspace,
\]
where $(I^1,\dots,I^t)[q(n)]$ is an oracle that answers at most $q(n)$ queries, and where every query of the form $(i,x)$ is answered by $I^i(x)$.
\end{enumerate}
\end{definition}

>>>>

\subsection{Obfuscation}
Our construction uses obfuscation for a family of point function $\mathcal{I} = \{I_w\}_{w \in \zo^*}$ defined as follows:
\[
I_w(x):\begin{cases} 1 & x=w\\0 & \text{otherwise}\end{cases}.
\]
The required notion of obfuscation is virtual grey-box (VGB) introduced in \cite{bitansky2010strong}. This notion is weaker then the standard notion of virtual black-box (\cite{barak2001possibility}) as it allows the simulator to run in unbounded time while making at most polynomial number of oracle queries to the function. In the following definition we also require that the obfuscation is composable and secure with respect to auxiliary input. Compassable auxiliary-input VGB obfuscators for point function are constructed in \cite[Theorem 6.1]{bitansky2010strong} from the Strong Vector Decision Difﬁe Hellman assumption which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points.

\begin{definition}[$t$-composable obfuscation VGB obfuscation with auxiliary input \cite{bitansky2010strong}]
\label{def:obf} Let $\mathcal{I}$ be a family of polynomial-size circuits.  A PPT algorithm $\mathcal{O}$ is a $t$-composable VGB obfuscator for $\mathcal{I}$ with auxiliary-input if the following conditions are met:
\begin{enumerate}
\item \emph{Functionality:} for every $I \in \mathcal{I}$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$.
\item \emph{Virtual grey-box:}  For every PPT adversary $A$ and polynomial $p$, there exists a (possibly inefficient) simulator $S$ and a polynomial $q$ such that for all sufficiently large $n$, any  sequence of circuits $I^1,\dots,I^t \in \mathcal{I}_n$, (where $t=\poly(n)$) and for all auxiliary inputs $z\in \zo^*$:
\[
|\Pr_{A,\mathcal{O}}[A(z,\mathcal{O}(I^1),\dots,\mathcal{O}(I^t)) = 1] - \Pr_{S}[S^{(I^1,\dots,I^t)[q(n)]}(z, 1^{|I^1|},\dots,1^{|I^t|}) = 1] | < \frac{1}{p(n)} \enspace,
\]
where $(I^1,\dots,I^t)[q(n)]$ is an oracle that answers at most $q(n)$ queries, and where every query of the form $(i,x)$ is answered by $I^i(x)$.
\end{enumerate}
\end{definition}
